\documentclass{londoncv}

% Import packages
\usepackage{nth}
\usepackage{hyperref}

% Set up document
\hypersetup{
  colorlinks=false,
  hidelinks,
  pdfauthor={Jane Doe},
  pdftitle={CV of Jane Doe}
}

% Begin document
\headertitle{Jane Doe \pipe Frontend Developer}
\headersubtitle{
	\icontext{\faEnvelope}{janedoe@email.co.uk} \pipe
	\icontext{\faPhone}{+44-1234568900} \pipe
	\icontext{\faMapMarker*}{London, United Kingdom} \\
	\icontext{\faGithub}{\href{https://www.github.com}{janedoe}} \pipe
	\icontext{\faKaggle}{\href{https://www.kaggle.com}{janedoe}} \pipe
	\icontext{\faLinkedin}{\href{https://www.linkedin.com/in/}{linkedin.com/in/jane-doe}} \pipe
}

\begin{document}
\maketitle

\skills
{
	\item Expertise in JavaScript, HTML5, CSS3, and ReactJS.
	\item Proficient in Redux, Node.js, and Express.js.
	\item Strong understanding of responsive design principles and cross-browser compatibility.
}
{
	\item Familiarity with version control systems (Git, SVN) and Agile methodologies.
	\item Excellent problem-solving abilities and attention to detail.
	\item Solid communication skills, both written and verbal.
}

\begin{cvcontainer}{Experience}



	\chronologicalitem
	{Jan. 2018--Present}
	{Frontend Software Developer}
	{XYZ Tech Ltd.}
	{London}
	{
	\begin{itemize}
		\item Collaborated with cross-functional teams to design, develop, and deploy user interfaces for web applications using ReactJS and Redux.
		\item Implemented and maintained responsive designs for desktop and mobile platforms.
		\item Contributed to the development of a company-wide style guide and component library.
	\end{itemize}
	}

	\chronologicalitem
	{May 2015--Dec. 2017}
	{Frontend Software Engineer}
	{ABC Solutions}
	{Manchester}
	{
	\begin{itemize}
		\item Developed and maintained user interfaces for various web applications using HTML5, CSS3, and JavaScript.
		\item Worked closely with designers to ensure adherence to brand guidelines and design specifications.
	\end{itemize}
	}

	\chronologicalitem
	{Aug 2013--Apr. 2015}
	{Junior Frontend Developer}
	{DEF Technologies}
	{Cardiff}
	{
	\begin{itemize}
		\item Assisted in the creation of user interfaces for web applications using jQuery and Bootstrap.
        	\item Tested and debugged frontend code to ensure proper functionality and compatibility across multiple browsers.
	\end{itemize}
	}
\end{cvcontainer}

\begin{cvcontainer}{Education}

	\chronologicalitem
	{2014--2015}
	{Master's Degree in Software Engineering}
	{University of Phonyville}
	{Birmingham}
	{
	\begin{itemize}
		\item Dissertation title: \textit{Frontend Architecture and Performance Optimization: Building Responsive User Interfaces with ReactJS and Redux}
	\end{itemize}
	}

	\chronologicalitem
	{2010--2013}
	{Bachelor of Science in Computer Science}
	{University of Fakeville}
	{Liverpool}
	{
	\begin{itemize}
		\item Awarded first-class honours.
	\end{itemize}
	}

\end{cvcontainer}

\begin{cvcontainer}{Certifications}
	\chronologicalitem
	{Mar. 2018}
	{ReactJS Developer Certification}
	{Fake Academy}
	{}
	{}

	\chronologicalitem
	{Feb. 2017}
	{Professional Scrum Master I (PSM I)}
	{Agile Institute}
	{}
	{}

	\chronologicalitem
	{Jun. 2015}
	{Full Stack Web Development Bootcamp Completion}
	{FakeCodeSchool}
	{}
	{}
\end{cvcontainer}

\end{document}
